Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
Div X tensor Q -> Q tensor Div X

\ssec{Adding Points}  \todo{Peter: Note to self: replace $H^0(X, \lfloor L\rfloor)$ with $H^0(\sx, L)$.}
\label{ssec:add-points}
%In this section, we prove various inductive statements under the following setup:
%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis). \todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph? Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial(I)$. We can even build this in to the macro possibly? }
Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
\begin{enumerate}
\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item $T\succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
\end{align*}
\end{enumerate}
Then,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
	+ \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
First, notice that $I'\subseteq I$ so 
\[
	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
\]

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{align}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
	N}.
\end{align}
Let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,

>>>>

\ssec{Adding Points}  \todo{Peter: Note to self: replace $H^0(X, \lfloor L\rfloor)$ with $H^0(\sx, L)$.}
\label{ssec:add-points}
%In this section, we prove various inductive statements under the following setup:
%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis). \todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph? Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial(I)$. We can even build this in to the macro possibly? }
Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.  This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan, \halfcan' \in \BQ \otimes \di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
\begin{enumerate}
\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item $T\succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
\end{align*}
\end{enumerate}
Then,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
	+ \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
First, notice that $I'\subseteq I$ so 
\[
	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
\]

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{align}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
	N}.
\end{align}
Let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,
